School accessibility: a new index applied to enrollment and performance inequalities

### 2015-09-28 paper.Rmd
Add equation

---
title: "School accessibility: a new index applied to enrollment and performance inequalities in Sao Paulo"
author: "Ana Moreno and Robin Lovelace"
date: "`r format(Sys.time(), '%F')`"
output: pdf_document
bibliography: school-access-bib.bib
---

@@

>>>>

---
title: 'School accessibility: a new index applied to enrollment and performance inequalities
  in Sao Paulo'
author: "Ana Moreno and Robin Lovelace"
output: pdf_document
bibliography: school-access-bib.bib
---

```{r, echo=FALSE}
#date: '`r format(Sys.time(), ''%F'')`'
```

@@

$$
\tau=2
$$
